Universal Anonymous Signatures

### 2022-05-12 prism-backend/research/gsac/model-uas.tex
Updated GSAC and UAS proofs based on updated non-frame definiton.
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.

From a functional perspective, we require that each issuer and opener fix
the issuance predicate \fissue and opener function \finsp when generating
their public keys. On the other hand, signature evaluation functions \feval can
be defined at signing time. This is in line with the usual practice in anonymous
credentials, that let
users prove arbitrary claims on their credentials, as long as they are met by
the contained attributes. In practice, most probably, the signing policy to be
employed in each signature will be defined by the verifier (or jointly between
user and verifier), including the specification of which inspector will be
able to post-process signatures\footnote{See, for instance, the concept of
  presentation exchanges, or requests, in the context of Verifiable Credentials:
  \url{https://identity.foundation/presentation-exchange/} (last access, May
  5th, 2022).}. Beyond these general policies, which already give much
flexibility, the syntax for \UAS supports multiple issuers and openers, and
lets users leverage multiple credentials to request issuance of new ones, and
to produce signatures.

@@

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. 
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.] Given global system
  parameters \parm, and function \finsp, an opener runs \OKeyGen to generate
  its opening key pair. The function \finsp defines the type of utility that
  will be extractable from signatures.
\item[$\usk \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's secret key.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle
  \Obtain(\usk,\lbrace (\cred_i,\ipk_i)\rbrace_{i \in \Issuers},\attrs),
  \Issue(\isk,\lbrace \ipk_i \rbrace_{i \in \Issuers},\attrs))
  \rangle$.] %
  This interactive protocol lets a user with key \usk running the
  \Obtain process, receive a credential \cred from an issuer in the system, on
  attribute set $\attrs$. The user leverages a set of $(\cred_i,\ipk_i)$ pairs,
  where $\cred_i$ is a credential obtained from the issuer with public
  key $\ipk_i$. The user outputs the produced credential \cred, while
  the issuer outputs the protocol transcript \utrans for the produced
  credential. To ease notation, we assume that the issuer public key associated
  to credential is available from the credential itself, and therefore
  omit the $\ipk_i$ values from the syntax, unless necessary to avoid
  ambiguity.
\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\lbrace (\cred_i,\ipk_i)
  \rbrace_{i \in \Issuers},\msg,\feval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credential-issuer pairs $(\cred_i,\ipk_i)$, a message \msg and evaluation
  function \feval, returns signature \sig and value \yeval.
\item[$1/0 \gets \Verify(\opk, \lbrace \ipk_i \rbrace_{i \in \Issuers},\sig,
  \yeval,\msg,\feval)$.] Checks whether $(\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys $\ipk_i$, for evaluation function \feval and inspector key \opk.
\item[$(\yinsp,\iproof)/\bot \gets \Open(\osk,\lbrace \ipk_i
  \rbrace_{i \in \Issuers},\sig,\yeval,\msg,\feval)$.] %
  Executed by the opener with private key \osk. Receives a signature $(\sig,
  \yeval)$ over message \msg and evaluation function \feval, generated using
  credentials issued by the issuers with public keys $\ipk_i$. If \sig is valid,
  the function outputs a value $\yinsp$.
\item[$1/0 \gets \Judge(\opk,\lbrace ipk_i \rbrace_{i \in \Issuers},\yinsp,
  \iproof,\sig,\yeval,\msg,\feval)$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $(\sig,\yeval)$ over
  message \msg, and for evaluation function \feval. 
\end{description}

\paragraph{Issuance, evaluation, and opening functions.} %
We emphasize that, both in our syntax definition, as well as on the following
modelling, we make use of three different and abstract functions: \fissue,
\feval and \finsp. The three functions are introduced to allow customized
governance of the resulting instantiation of an \UAS scheme. They will be
defined by different parties, but in all cases, they are run by users (maybe,
on user-private data). Also, in all cases, the user has to prove correctness of
their computation. We introduce them next, \todo{and will give concrete examples
  in \secref{sec:uas-instantiation}.}

@@

We emphasize that, even though \finsp and \feval seem redundant, they are not.
To see this, observe that \finsp is defined by inspectors, and will be fixed in
all signatures that can be opened by the opener who defined it. On the other
hand, \feval can be defined by (e.g.) verifiers on a per-signature basis, even
if the signatures use the same \finsp. Thus, \feval can be programmed to contain
the conditions set by (e.g.) verifiers for signatures they receive; whereas
\finsp can be programmed to extract specific utility values when needed, which
may depend on the checks required by the verifier a signature was intended to.

@@

Note that, for all the helper functions, in the case of credentials, transcripts,
and signatures by honest users, it is enough to have access to the corresponding
state information (described below) maintained by the challenger in our
experiments. For credentials and join transcripts of corrupt users, or
dishonestly produced signatures, we do need to perform actual extraction. How to
do this will depend on each specific construction. Certainly, the challenger
needs special knowledge/power such as decryption trapdoors, the ability to
rewind the game, or program random oracles. The approach needs thus to depend on
the concrete construction. \todo{Although, for the case of \ExtractIssue,
online extractability \needcite (or alternative requirements, such as
non-parallel or logarithmic number of joins) is necessary.}

@@

\begin{description}
\item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
  the associated issuance function.
\item[\OGEN.] Adds a new inspector to the game, generating its key pair and
  setting the associated evaluation and inspection functions.
\item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
  key to the adversary.
\item[\OCORR.] Corrupts an existing (and honest) inspector, by giving its secret
  key to the adversary.  
\item[\HUGEN.] Adds a new honest user to the game, by honestly generating
  the user's key pair.
\item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
  user already exists and is honest, corrupts it.
\item[\RREG.] Reads the given transcript table entry.
\item[\WREG.] Sets a transcript table entry to the given value.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer
  in games that support it, by letting it interact with honest users who want to
  receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures from credentials belonging
  to honest users.
\item[\OPEN.] Given an honestly produced signature, outputs the result of the
  opening function, along with a correctness proof.
\item[\CHALb.] Upon receiving two challenge users and credential sets, a common
  singing evaluation function and a message, returns a signature produced by one
  of these two user and credential sets, defined by the bit $b$, which is
  established in the anonymity game.
\end{description}

@@

    \caption{Detailed oracles available in our model (1/2). Oracles for
      generating key material for users, issuers, and inspectors.}
    \label{fig:oracles1}
  \end{figure*}
}

@@

        \procedure{$\OPEN(\oid,\sig,\yeval,\msg)$}{%
          \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\sig,\yeval,\msg,\feval)
          \in \SIG[\uid] \\
          (\yinsp,\iproof) \gets
          \Inspect(\PRVOK[\oid],\GK[\scid],\sig,\yeval,\msg,\feval) \\
          \pcif \CSIG[\sig] \neq \bot: \\
          \pcind \textrm{Parse $\CSIG[\sig]$ as $(\oid,\cuid_b,\scid_b,\msg,
            \feval,\yeval$} \\
          \hspace*{83pt}\cuid_{1-b},\csig_{1-b},\scid_{1-b}) \\
          \pcind (\yinsp',\iproof') \gets
          \Inspect(\PRVOK[\oid],\IK[\siid],\\
          \hspace*{107pt} \sig_{1-b},\msg,\feval) \\
          \pcind \pcif \yinsp' \neq \yinsp: \pcreturn \bot \\
          \pcreturn (\yinsp,\iproof)
        }

@@

\begin{figure}[htp!]
  \procedure{$\ExpCorrect(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\uid,\oid,\scid,\msg,\feval)
    \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS,\RREG}(\parm) \\
    \pcif \feval \notin \famfeval: \pcreturn 0 \\
    \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
    (\sig,\yeval) \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\sig,\msg,\feval) = 0: \pcreturn 1 \\
    \pcfor \cid \in \scid \pcdo: \\
    \pcind \textrm{Let}~\scred^{\cid}~\textrm{be the credentials used to obtain}
    ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,\fissue^{\cid}),\cdot)\\
    \pcind \pcif \fissue^{\cid}(\UK[\uid],\scred^{\cid},\ATTR[\cid]) = 0: \pcreturn 1 \\
    \pcif \feval(\UK[\uid],\CRED[\scid],\msg) \neq \yeval: \pcreturn 1 \\
    (\yinsp,\iproof) \gets \Inspect(\PRVOK[\gid],\PUBIK[\scid],\sig,\msg,\feval) \\
    \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\y,\iproof,\sig,\yeval,\msg,\feval)
    = 0 \lor \yinsp \neq \finsp^\gid(\yeval,\UK[\uid],\CRED[\scid],\msg)): \\
    \pcind \pcreturn 1 \\
    \pcreturn 0
  }  
  \caption{Correctness experiment for \UAS schemes.}
  \label{fig:exp-uas-corr}
\end{figure}

@@

Note that we could actually remove the requirement that the evaluation function
has to produce the same output on both challenge user-credentials pairs.
However, by doing so, we would force all constructions to maintain private the
output of \feval. We opt not to require that, though, as it directly allows
our model to cover interesting use cases -- such as restricting to selective
disclosure, or privacy-preserving variants of functional signatures \todo{check
  the latter, and perhaps expand}.

@@

\begin{figure}[htp!]
    \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\oid,\siid,\sig,\yeval,\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
      \pcif \exists \uid~\st~(\cdot,\cdot,\sig,\yeval,\msg,\feval) \in
      \SIG[\uid]: \pcreturn 0 \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\sig,\yeval,\msg,\feval) = 0:
      \pcreturn 0 \\
      (\yinsp,\iproof) \gets \Inspect(\PRVOK[\oid],\siid,\sig,\yeval,\msg) \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\sig,\yeval,\msg,\feval)
      = 0: \pcreturn 1 \\
      (\usk,\scred,\attrs_{\scred},\yinsp',r) \gets \ExtractSign(\oid,\siid,\sig,
      \yeval,\msg,\feval) \\
      \pcif \feval(\usk,\scred,\msg) \neq \yeval: \pcreturn 1 \\
      \pcif \finsp(\yeval,\usk,\scred,\msg) \neq \yinsp \lor \yinsp \neq \yinsp':
      \pcreturn 1 \\
      \pcif \exists \cred \in \scred~\st~\IdentifyCred(\usk,\attrs_{\cred},\cred) = 0:
      \pcreturn 1 \\
      \pcif \nexists \uid~\st~\IdentifyUK(\uid,\usk) = 1: \pcreturn 1 \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of signatures in \UAS schemes.}
  \label{fig:exp-uas-unfor-sign}
\end{figure}

@@

\paragraph{Non-frameability.} %
Non-frameability variants are a core unforgeability-type property in group
signatures. However, no similar property is modeled for anonymous credentials
(\todo{see the discussion in \secref{sec:introduction} for further detail. Also,
consider conditional anonymity notions pointed to by Elizabeth}). It is a quite
strong property, as it must be ensured even in the presence of dishonest issuer
and opener. Intuitively, it prevents the adversary from creating a signature
that can be (even in some generic sense) associated to an honest user who did
not produce it. Depending on the opening capabilities of the scheme,
this framing could be done in different ways; i.e., by convincing third parties
that signatures by different (possibly corrupt) users are linked, or directly
by having opening proofs output the identity of a user who did not create the
signature being opened.

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\oid,\siid,\sig,\yeval,\msg,\feval,\yinsp,\iproof) \gets
    \adv^{\Oframe}(\parm) \\
    \pcif \exists \uid~\st~(\cdot,\cdot,\sig,\yeval,\msg,\feval) \in \SIG[\uid]:
    \pcreturn 0 \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\sig,\yeval,\msg,\feval) = 0:
    \pcreturn 0 \\
    \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\sig,\yeval,\msg) = 0:
    \pcreturn 0 \\
    (\usk,\scred,\attrs_{\scred},\yinsp',r) \gets
    \ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \\
    \pcif \exists \uid \in \HU~\st~\UK[\uid] = \usk: \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Experiment for non-frameability on \UAS schemes.}
  \label{fig:exp-uas-frame}
\end{figure}

>>>>

From a functional perspective, we require that each issuer and opener fix
the issuance predicate \fissue and opener function \finsp when generating
their public keys. On the other hand, signature evaluation functions \feval can
be defined at signing time. This is in line with the usual practice in anonymous
credentials, that let
users prove arbitrary claims on their credentials, as long as they are met by
the contained attributes. In practice, most probably, the signing policy to be
employed in each signature will be defined by the verifier (or jointly between
user and verifier), including the specification of which opener will be
able to post-process signatures\footnote{See, for instance, the concept of
  presentation exchanges, or requests, in the context of Verifiable Credentials:
  \url{https://identity.foundation/presentation-exchange/} (last access, May
  5th, 2022).}. Beyond these general policies, which already give much
flexibility, the syntax for \UAS supports multiple issuers and openers, and
lets users leverage multiple credentials to request issuance of new ones, and
to produce signatures.

@@

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. 
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.] Given global system
  parameters \parm, and function \finsp, an opener runs \OKeyGen to generate
  its opening key pair. The function \finsp defines the type of utility that
  will be extractable from signatures.
\item[$\usk \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's secret key.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle
  \Obtain(\usk,\lbrace (\cred_i,\ipk_i)\rbrace_{i \in \Issuers},\attrs),
  \Issue(\isk,\lbrace \ipk_i \rbrace_{i \in \Issuers},\attrs))
  \rangle$.] %
  This interactive protocol lets a user with key \usk running the
  \Obtain process, receive a credential \cred from an issuer in the system, on
  attribute set $\attrs$. The user leverages a set of $(\cred_i,\ipk_i)$ pairs,
  where $\cred_i$ is a credential obtained from the issuer with public
  key $\ipk_i$. The user outputs the produced credential \cred, while
  the issuer outputs the protocol transcript \utrans for the produced
  credential. To ease notation, we assume that the issuer public key associated
  to credential is available from the credential itself, and therefore
  omit the $\ipk_i$ values from the syntax, unless necessary to avoid
  ambiguity.
\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\lbrace (\cred_i,\ipk_i)
  \rbrace_{i \in \Issuers},\msg,\feval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credential-issuer pairs $(\cred_i,\ipk_i)$, a message \msg and evaluation
  function \feval, returns signature \sig and value \yeval.
\item[$1/0 \gets \Verify(\opk, \lbrace \ipk_i \rbrace_{i \in \Issuers},\sig,
  \yeval,\msg,\feval)$.] Checks whether $(\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys $\ipk_i$, for evaluation function \feval and opener key \opk.
\item[$(\yinsp,\iproof)/\bot \gets \Open(\osk,\lbrace \ipk_i
  \rbrace_{i \in \Issuers},\sig,\yeval,\msg,\feval)$.] %
  Executed by the opener with private key \osk. Receives a signature $(\sig,
  \yeval)$ over message \msg and evaluation function \feval, generated using
  credentials issued by the issuers with public keys $\ipk_i$. If \sig is valid,
  the function outputs a value $\yinsp$.
\item[$1/0 \gets \Judge(\opk,\lbrace ipk_i \rbrace_{i \in \Issuers},\yinsp,
  \iproof,\sig,\yeval,\msg,\feval)$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $(\sig,\yeval)$ over
  message \msg, and for evaluation function \feval. 
\end{description}

\paragraph{Issuance, evaluation, and opening functions.} %
We emphasize that, both in our syntax definition, as well as on the following
modelling, we make use of three different and abstract functions: \fissue,
\feval and \finsp. The three functions are introduced to allow customized
governance of the resulting instantiation of an \UAS scheme. They will be
defined by different parties, but in all cases, they are run by users (maybe,
on user-private data). Also, in all cases, the user has to prove correctness of
their computation. We introduce them next, and give concrete examples for
building specific well-known restrictions of \UAS in
\secref{sec:transformations}.

@@

We emphasize that, even though \finsp and \feval seem redundant, they are not.
To see this, observe that \finsp is defined by openers, and will be fixed in
all signatures that can be opened by the opener who defined it. On the other
hand, \feval can be defined by (e.g.) verifiers on a per-signature basis, even
if the signatures use the same \finsp. Thus, \feval can be programmed to contain
the conditions set by (e.g.) verifiers for signatures they receive; whereas
\finsp can be programmed to extract specific utility values when needed, which
may depend on the checks required by the verifier a signature was intended to.

@@

Note that, for all the helper functions, in the case of credentials, transcripts,
and signatures by honest users, it is enough to have access to the corresponding
state information (described below) maintained by the challenger in our
experiments. For credentials and join transcripts of corrupt users, or
dishonestly produced signatures, we do need to perform actual extraction. How to
do this will depend on each specific construction. Certainly, the challenger
needs special knowledge/power such as decryption trapdoors, the ability to
rewind the game, or program random oracles. The approach needs thus to depend on
the concrete construction. \jdv{Although, for the case of \ExtractIssue,
  online extractability (or alternative requirements, such as non-parallel or
  logarithmic number of joins) is necessary.}

@@

\begin{description}
\item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
  the associated issuance function.
\item[\OGEN.] Adds a new opener to the game, generating its key pair and
  setting the associated evaluation and inspection functions.
\item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
  key to the adversary.
\item[\OCORR.] Corrupts an existing (and honest) opener, by giving its secret
  key to the adversary.  
\item[\HUGEN.] Adds a new honest user to the game, by honestly generating
  the user's key pair.
\item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
  user already exists and is honest, corrupts it.
\item[\RREG.] Reads the given transcript table entry.
\item[\WREG.] Sets a transcript table entry to the given value.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer
  in games that support it, by letting it interact with honest users who want to
  receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures from credentials belonging
  to honest users.
\item[\OPEN.] Given an honestly produced signature, outputs the result of the
  opening function, along with a correctness proof.
\item[\CHALb.] Upon receiving two challenge users and credential sets, a common
  singing evaluation function and a message, returns a signature produced by one
  of these two user and credential sets, defined by the bit $b$, which is
  established in the anonymity game.
\end{description}

@@

    \caption{Detailed oracles available in our model (1/2). Oracles for
      generating key material for users, issuers, and openers.}
    \label{fig:oracles1}
  \end{figure*}
}

@@

        \procedure{$\OPEN(\oid,\sig,\yeval,\msg)$}{%
          \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\sig,\yeval,\msg,\feval)
          \in \SIG[\uid] \\
          (\yinsp,\iproof) \gets
          \Open(\PRVOK[\oid],\GK[\scid],\sig,\yeval,\msg,\feval) \\
          \pcif \CSIG[\sig] \neq \bot: \\
          \pcind \textrm{Parse $\CSIG[\sig]$ as $(\oid,\cuid_b,\scid_b,\msg,
            \feval,\yeval$} \\
          \hspace*{83pt}\cuid_{1-b},\csig_{1-b},\scid_{1-b}) \\
          \pcind (\yinsp',\iproof') \gets
          \Open(\PRVOK[\oid],\IK[\siid],\\
          \hspace*{107pt} \sig_{1-b},\msg,\feval) \\
          \pcind \pcif \yinsp' \neq \yinsp: \pcreturn \bot \\
          \pcreturn (\yinsp,\iproof)
        }

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpCorrect(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\uid,\oid,\scid,\msg,\feval)
    \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS,\RREG}(\parm) \\
    \pcif \feval \notin \famfeval: \pcreturn 0 \\
    \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
    (\sig,\yeval) \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\sig,\msg,\feval) = 0: \pcreturn 1 \\
    \pcfor \cid \in \scid \pcdo: \\
    \pcind \textrm{Let}~\scred^{\cid}~\textrm{be the credentials used to obtain}
    ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,\fissue^{\cid}),\cdot)\\
    \pcind \pcif \fissue^{\cid}(\UK[\uid],\scred^{\cid},\ATTR[\cid]) = 0: \pcreturn 1 \\
    \pcif \feval(\UK[\uid],\CRED[\scid],\msg) \neq \yeval: \pcreturn 1 \\
    (\yinsp,\iproof) \gets \Open(\PRVOK[\gid],\PUBIK[\scid],\sig,\msg,\feval) \\
    \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\y,\iproof,\sig,\yeval,\msg,\feval)
    = 0 \lor \yinsp \neq \finsp^\gid(\yeval,\UK[\uid],\CRED[\scid],\msg)): \\
    \pcind \pcreturn 1 \\
    \pcreturn 0
  }  
  \caption{Correctness experiment for \UAS schemes.}
  \label{fig:exp-uas-corr}
\end{figure}

@@

Note that we could actually remove the requirement that the evaluation function
has to produce the same output on both challenge user-credentials pairs.
However, by doing so, we would force all constructions to maintain private the
output of \feval. We opt not to require that, though, as it directly allows
our model to cover interesting use cases -- such as restricting to selective
disclosure, or privacy-preserving variants of functional signatures \jdv{check
  the latter, and perhaps expand}.

@@

\begin{figure}[htp!]
    \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\oid,\siid,\sig,\yeval,\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
      \pcif \exists \uid~\st~(\cdot,\cdot,\sig,\yeval,\msg,\feval) \in
      \SIG[\uid]: \pcreturn 0 \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\sig,\yeval,\msg,\feval) = 0:
      \pcreturn 0 \\
      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\sig,\yeval,\msg) \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\sig,\yeval,\msg,\feval)
      = 0: \pcreturn 1 \\
      (\usk,\scred,\attrs_{\scred},\yinsp',r) \gets \ExtractSign(\oid,\siid,\sig,
      \yeval,\msg,\feval) \\
      \pcif \feval(\usk,\scred,\msg) \neq \yeval: \pcreturn 1 \\
      \pcif \finsp(\yeval,\usk,\scred,\msg) \neq \yinsp \lor \yinsp \neq \yinsp':
      \pcreturn 1 \\
      \pcif \exists \cred \in \scred~\st~\IdentifyCred(\usk,\attrs_{\cred},\cred) = 0:
      \pcreturn 1 \\
      \pcif \nexists \uid~\st~\IdentifyUK(\uid,\usk) = 1: \pcreturn 1 \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of signatures in \UAS schemes.}
  \label{fig:exp-uas-unfor-sign}
\end{figure}

@@

\paragraph{Non-frameability.} %
Non-frameability variants are a core unforgeability-type property in group
signatures. However, no similar property is modeled for anonymous credentials.
It is a quite strong property, as it must be ensured even in the presence of
dishonest issuer and opener. Intuitively, it prevents the adversary from
creating a signature that can be (even in some generic sense) associated to an
honest user who did not produce it. Depending on the opening capabilities of the
scheme, this framing could be done in different ways; i.e., by convincing third
parties that signatures by different (possibly corrupt) users are linked, or
directly by having opening proofs output the identity of a user who did not
create the signature being opened.

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\oid,\siid,\sig,\yeval,\msg,\feval,\yinsp,\iproof) \gets
    \adv^{\Oframe}(\parm) \\
%    \pcif \exists \uid~\st~(\cdot,\cdot,\sig,\yeval,\msg,\feval) \in \SIG[\uid]:
%    \pcreturn 0 \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\sig,\yeval,\msg,\feval) = 0:
    \pcreturn 0 \\
    \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\sig,\yeval,\msg) = 0:
    \pcreturn 0 \\
    (\usk,\scred,\attrs_{\scred},\yinsp',r) \gets
    \ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \\
    \pcif \exists \uid \in \HU~\st~\UK[\uid] = \usk~\land \\
    \pcind (\nexists (\cdot,\cdot,\sig,\yeval,\msg,\feval) \in \SIG[\uid]
    \lor \yinsp \neq \yinsp'): \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Experiment for non-frameability on \UAS schemes.}
  \label{fig:exp-uas-frame}
\end{figure}
